Cognitive Analysis

### 2024-07-25 Manuscript Analysis/manuscript_analysis.Rmd
wm model

### Initial Model

@@

wm_pupil <- bam(normed_pupil ~ condition +
                  s(time_norm, by = condition, k = 25) +
                  te(time_norm, list_sort_c, k = 20) +
                  # Random Smooth for listener
                  s(time_norm, listener, bs = 'fs', m = 1),
                discrete = T,
                AR.start = start_event,
                rho = .9341941,
                family = "scat",
                data = pupil)

@@

@@

### Model 1

@@

wm_pupil_1 <- bam(normed_pupil ~ condition +
                  s(time_norm, by = condition, k = 25) +
                  te(time_norm, list_sort_c, by = speaker, k = 20) +
                  # Random Smooth for listener
                  s(time_norm, listener, bs = 'fs', m = 1),
                discrete = T,
                AR.start = start_event,
                rho = .9341941,
                family = "scat",
                data = pupil)

summary.gam(wm_pupil_1)

@@

gam.check(wm_pupil_1)

acf_resid(wm_pupil_1)

compareML(m0_pupil, wm_pupil_1, signif.stars = T, suggest.report = T)

```
### Model 2

wm_pupil_2 <- bam(normed_pupil ~ condition +
                  s(time_norm, by = condition, k = 25) +
                  te(time_norm, list_sort_c, by = condition, k = 20) +
                  # Random Smooth for listener
                  s(time_norm, listener, bs = 'fs', m = 1),
                discrete = T,
                AR.start = start_event,
                rho = .9341941,
                family = "scat",
                data = pupil)

summary.gam(wm_pupil_2)

gam.check(wm_pupil_2)

acf_resid(wm_pupil_2)

```
#### Model Comparison

compareML(m0_pupil, wm_pupil_2, signif.stars = T, suggest.report = T)

>>>>

@@

wm_pupil <- bam(normed_pupil ~ condition +
                  s(time_norm, by = condition, k = 25) +
                  s(list_sort_c, by = condition, k = 20) +
                  # Random Smooth for listener
                  s(time_norm, listener, bs = 'fs', m = 1),
                discrete = T,
                AR.start = start_event,
                rho = .9341941,
                family = "scat",
                data = pupil)

@@

plot_diff(wm_pupil, view = "list_sort_c",
          comp = list(condition = c("ALS Inaccurate", "ALS Accurate")))

plot_diff(wm_pupil, view = "list_sort_c",
          comp = list(condition = c("Control Inaccurate", "Control Accurate")))

plot_diff(wm_pupil, view = "list_sort_c",
          comp = list(condition = c("ALS Accurate", "Control Accurate")))

@@

@@

wm_pred <- expand_grid(
  time_norm = seq(from=min(pupil$time_norm), 
              to=max(pupil$time_norm), 
              length.out = 100),
  list_sort_c = seq(from=min(pupil$list_sort_c), 
              to=max(pupil$list_sort_c), 
              length.out = 100),
  condition = c("Control Accurate", "Control Inaccurate", "ALS Accurate", "ALS Inaccurate"),
  listener = c("LE01", "LE02", "LE04", "LE05", "LE06", "LE07", "LE08", "LE09", "LE10", "LE11",
               "LE12", "LE13", "LE15", "LE16", "LE18", "LE19", "LE20", "LE21", "LE22", "LE23",
               "LE24", "LE25", "LE26", "LE27", "LE28", "LE29", "LE30", "LE31", "LE32", "LE33", 
               "LE34", "LE35", "LE36", "LE38")
)

wm_pred <- predict(wm_pupil, newdata = wm_pred, 
                      se.fit = TRUE) |> 
  as_tibble() |>
  cbind(wm_pred)

@@
